---
output: rmarkdown::github_document
---
`mtblr` : Tools to work with [`mtbl`](https://github.com/farsightsec/mtbl) files in R

`mtbl` is a C library implementation of the Sorted String Table (SSTable) data
structure, based on the SSTable implementation in the open source [Google
LevelDB library](http://code.google.com/p/leveldb/). An SSTable is a file
containing an immutable mapping of keys to values. Keys are stored in sorted
order, with an index at the end of the file allowing keys to be located quickly.

`mtbl` is not a database library. It does not provide an updateable key-value
data store, but rather exposes primitives for creating, searching and merging
SSTable files. Unlike databases which use the SSTable data structure internally
as part of their data store, management of SSTable files -- creation, merging,
deletion, combining of search results from multiple SSTables -- is left to the
discretion of the `mtbl` library user.

The following functions are implemented:

- `read_mtbl`: Open an mtbl file
- `mtbl_length`: Retrieve the number of records in an open mtbl file
- `close_mtbl`:	Close an mtbl file
- `mtbl_map`:	Start an iterator over an mtbl file
- `mtbl_next`: Iterate over mtbl file entries
- `mtbl_iter_close`: Close an iterator when finished
- `mtbl_get`:	Retrieve a key/value pair from an mtbl by key
- `mtbl_get_prefix`: Retrieve value(s) for a given key in an mtbl
- `mtbl_keys`: Return all the keys of an mtbl
- `mtbl_values`: Return all the values of an mtbl

The following data sets are included:

- `system.file("extdata/sample.mtbl", package="mtblr")`

### News

```{r child='NEWS.md'}
```

### Installation

```{r eval=FALSE}
devtools::install_github("brudis-r7/mtblr")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(mtblr)

# current verison
packageVersion("mtblr")

mtbl <- read_mtbl(system.file("extdata/sample.mtbl", package="mtblr"))

mtbl_length(mtbl)

head(mtbl_keys(mtbl))

head(mtbl_values(mtbl))

mtbl_next(mtbl_map(mtbl))[99][[1]]$value

mtbl_next(mtbl_get(mtbl, "aa"))[[1]]$value

mtbl_next(mtbl_get_prefix(mtbl, "a"))[[10]]$value
```

### Test Results

```{r}
library(mtblr)
library(testthat)

date()

test_dir("tests/")
```

